### 2019-03-15 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

where $C_L$ is the car length. When the velocity is zero then the rate of change of heading angle is zero, that is, it is not possible to change the vehicle's orientation
when it is not moving. If the front wheel is orthogonal to the back wheel, i.e. the steering angle is $\frac{\pi}{2}$, the ATLASCAR2 cannot move forward and the model enters an undefined region. In order to simplify the model, it is assumed that only the front wheel can be steered. Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance. Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle. In particular the rate of change of heading angle is referred to as turn rate which can be evaluated with a gyroscope. This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius. We can write the non-holonomic constraint which is an expression for velocity in the vehicle's $y$-direction in the world coordinate frame as follows:
\begin{equation}
	\dot{y}\cos\theta-\dot{x}\cos\theta=0
\end{equation}
This equation cannot be integrated to form a
relationship between $x,y$ and $\theta$.

@@

@@

@@

% RESULTS BRAKING THREE OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_braking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Figure \ref{fig:braking}.}
	\label{fig:components}
\end{figure}

>>>>

where $C_L$ is the car length. When the velocity is zero then the rate of change of heading angle is zero, that is, it is not possible to change the vehicle's orientation
when it is not moving. If the front wheel is orthogonal to the back wheel, i.e. the steering angle is $\frac{\pi}{2}$, the ATLASCAR2 cannot move forward and the model enters an undefined region. In order to simplify the model, it is assumed that only the front wheel can be steered. Moreover, in this chapter it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance. Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle. In particular the rate of change of heading angle is referred to as turn rate which can be evaluated with a gyroscope. This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius. We can write the non-holonomic constraint which is an expression for velocity in the vehicle's $y$-direction in the world coordinate frame as follows:
\begin{equation}
	\dot{y}\cos\theta-\dot{x}\cos\theta=0.
\end{equation}

This equation cannot be integrated to form a
relationship between $x,y$ and $\theta$.

@@

% RESULTS ONE MOVING OBSTACLE
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_one_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
	\label{fig:components_one_moving_obstacle}
\end{figure}

@@

% SIX MOVING OBSTACLES
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_6.pdf}
	\end{minipage}
	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
	\label{fig:obstacleAvoidance_six_obstacles}
\end{figure}

% RESULTS SIX MOVING OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_six_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of overtaking with six moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_six_obstacles}.}
	\label{fig:components_six_moving_obstacles}
\end{figure}

\subsection{No Overtaking}
%NO OVERTAKING
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_4.pdf}
	\end{minipage}
	\caption{Simulation of no overtaking with three moving obstacles that move in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_no_overtaking}
\end{figure}

% RESULTS NO OVERTAKING
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_no_overtaking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of no overtaking with three moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_no_overtaking}.}
	\label{fig:components_no_overtaking}
\end{figure}

@@

% RESULTS BRAKING THREE OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_braking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Figure \ref{fig:braking}.}
	\label{fig:components}
\end{figure}
